\boldmath Commissioning of the highly granular SiW-ECAL technological prototype

### 2018-06-13 performance-paper-draft/longversion/draft.tex
2nd iteration long paper: correct the summary and other minor changes

The R\&D program of the highly granular SiW-ECAL detector is in an exciting phase. 
After the proof of principle of the imaging calorimetry concept using the physics prototype, the 
technological prototype is being constructed and tested. In this document we describe the commissioning and
beam test performance of a prototype built in with the first fully assembled
detector elements.

A very comprehensive and detailed commissioning procedure has been established and optimized
allowing us to identify and isolate the different noise sources that could spoil the data taking.
The beam test has provided a lot of useful data to study 
the performance of the detector and  to perform
a channel by channel calibration.
A full analysis of the MIP calibration within magnetic field and
the response of the prototype in electromagnetic shower events
will be covered in a future document.
In addition, the results shown here serve as input
for ongoing and future R\&D.

>>>>

The R\&D program of the highly granular SiW-ECAL detector is in an exciting phase. 
After the proof of principle of the imaging calorimetry concept using the physics prototype, the 
technological prototype is being constructed and tested. In this document we describe the commissioning and
beam test performance of a prototype built in with the first fully assembled
detector elements, in contrast with previous beam tests. In addition,
with the setup used in this beam test we reached levels of granularity
similar to the targets of the ILD detector for the ILC. This is also the first time
that a SiW-ECAL prototype continuously takes data in a beam test running in power pulsing mode, one of the crucial
features for the detectors for the ILC. Finally, we tested the performance of the detector
modules working for long periods inside magnetic fields.

A very comprehensive and detailed commissioning procedure has been established and optimized
allowing us to identify and isolate the different noise sources that could spoil the data taking.
The beam test has provided a lot of useful data to study 
the performance of the detector and to perform
a channel by channel calibration, showing a good homogenity with a spread of the 5\% for all channels.
The signal over noise of the detector has been evaluated to be 12.8 for the trigger
decission and 20.4 for the charge measurement using, in both cases, MIP signals as reference.
